{\LARGE Model Selection for Scalar-on-Function Regression \\ with Applications to Near-Infrared Spectroscopy}

### 2022-02-02 Paper/main.tex
Small correction

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator. Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t)
	\end{equation}

@@

	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi_{j}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
	\begin{equation}
		X(t) = \mu(t) + \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
	\end{equation}
	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} X(t)(\omega) \nu_{j}(t)dt$. These coefficients satisfy the following conditions.
	\begin{enumerate}
		\item $\mathbb{E}[\xi_{j}] = 0$
		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
		\item Var[$\xi_{j}$] = $\lambda_{j}$
	\end{enumerate}

	\begin{proof}
		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$. With the solution that $\xi_{j}(\omega) = \int_{0}^{1} X(\omega)(t) \nu_{j}(t)dt$ satisfy the three conclusions by Lemma \ref{Proof1}, We prove this expansion by considering
		\begin{equation}
			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
			= \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
		\end{equation}
		where $F(t)$ is the centered process of $X(t)$.
		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
		\begin{equation}\label{Thr1}
			\begin{split}
				\epsilon_{n}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} 	\nu_{j}(t)\bigg)^2 \right]\\
				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{j=1}^{n}\xi_{j}\nu_{j}(t)\bigg] + \mathbb{E}\bigg[\sum_{j=1}^{n}\sum_{k=1}^{n}\xi_{j}\xi_{k}\nu_{j}(t)\nu_{k}(t)\bigg]
			\end{split}
		\end{equation}

>>>>

	\begin{equation}\label{CovarianceFunction}
		c(t,s) = \mathbb{E}\big[ \left( X(\omega)(t) - \mu(t) \right) \left( X(\omega)(s) - \mu(s) \right) \big]
	\end{equation}
	where the $c(t,s)$ are Hilbert-Shmidt Kernels defined through $c : [0,1] \times [0,1] \rightarrow \mathbb{R}$. Let $K$ be the integral operater on $\mathbb{L}^{2}[0,1]$ such that $K : \nu \rightarrow K \nu$ for $\nu \in \mathbb{L}^{2}[0,1]$, by
	\begin{equation}
		[K \nu](t) = \int_{0}^{1}c(t,s) \nu(s)ds = \lambda \nu(t)
	\end{equation}

	Then, the operator $K$ has orthonormal basis functions $\nu_{i} \in \mathbb{L}^{2}[0,1]$ corresponding to eigenvalues $\lambda_{i}$ for all $i$ since it is a positive compact self-adjoint operator(cf. \cite{alexanderian_KLexpansion_2015}). Moreover, $K$ holds that the eigenvalues can be ordered in nonincreasing order as follows $\lambda^{1} \geq \lambda^{2} \geq \dots \geq 0$ where the superscript is not the power but index. Therefore, the functions $X$ are approximated enough well by first few principal components since the order of them are sorted in descending order of eigenvalues corresponding to the eigenfunctions (e.g. $Var(\xi^{m}) \geq Var(\xi^{n})$ for all $m < n$). Theoretical considerations lead to the result that $X$ can be represented in the following form, called its Karhunen-Lo\'{e}ve expansion. The proofs are provided at \ref{Proof1} and \ref{Proof2}.

@@

	\begin{equation}\label{KarhunenLoeve}
		X(\omega)(t) = \mu(t) + \sum_{m \in \mathbb{R}} \xi^m(\omega) \nu^m(t), \quad \xi^m(\omega) =  \int_{0}^{1} \left(X(\omega)(s) - \mu(s)\right) \nu^m(s) \mathrm{d}s
	\end{equation}

@@

	\subsection{Theorem (Karhunen-Lo\'{e}ve expansion)} \label{Proof2}
	Let $X : [0,1]  \rightarrow \mathbb{R}$ be a mean-square continuous stochastic process with $X \in \mathbb{L}^{2}[0,1]$. Then there exists a basis ${\xi_{j}}$ of $\mathbb{L}^2[0,1]$ such that for all $t \in [0,1]$,
	\begin{equation}
		X(t) = \mu(t) + \sum_{j=1}^{\infty} \xi_{j} \nu_{j}(t),
	\end{equation}
	where $\mu(t)$ is the mean function of $X(t)$ and coefficients $\xi_{j}$ are given by $\xi_{j}(\omega) = \int_{0}^{1} (X(t)(\omega) - \mu(t)) \nu_{j}(t)dt$. These coefficients satisfy the following conditions.
	\begin{enumerate}
		\item $\mathbb{E}[\xi_{j}] = 0$
		\item $\mathbb{E}[\xi_{j} \xi_{k}] = \lambda_{j}$, if $j = k$, otherwise 0
		\item Var[$\xi_{j}$] = $\lambda_{j}$
	\end{enumerate}

	\begin{proof}
		We know that $K$ has a complete set of eigenvectors ${\nu_{j}}$ in $\mathbb{L}^{2}[0,1]$ and non-negative eigenvalues $\lambda_{j}$. With the reminder that $\xi_{j}(\omega)$ satisfy the three conclusions by Lemma \ref{Proof1}, we prove this expansion by considering
		\begin{equation}
			\epsilon_{n}(t) := \mathbb{E} \left[\bigg( X(t) -\mu(t)- \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
			= \mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} \nu_{j}(t)\bigg)^2 \right]
		\end{equation}
		where $F(t)$ is the centered process of $X(t)$.
		Once it is shown that $\lim\limits_{n \rightarrow \infty} \epsilon_{n}(t) = 0$ uniformly in [0,1], the proof is completed.
		\begin{equation}\label{Thr1}
			\begin{split}
				\epsilon_{n}(t) = &\mathbb{E} \left[\bigg( F(t) - \sum_{j=1}^{n} \xi_{j} 	\nu_{j}(t)\bigg)^2 \right]\\
				= & \mathbb{E}[F(t)^{2}] - 2\mathbb{E}\bigg[F(t)\sum_{j=1}^{n}\xi_{j}\nu_{j}(t)\bigg] + \mathbb{E}\bigg[\sum_{j=1}^{n}\sum_{k=1}^{n}\xi_{j}\xi_{k}\nu_{j}(t)\nu_{k}(t)\bigg]
			\end{split}
		\end{equation}
